Theories of deliberated judgment

### 2022-08-06 simple.tex
Started using P instead of Phi

\section{Exposure protocol and deliberated choice}
Let $\Phi = \set{\phi, ¬\phi}$ represent the decision at stake. The set $\Phi$ represents two antagonistic acts, such as “buy this object for the price of \$15” and “do not buy this object for the price of \$15”, or “take this job offer” and “decline this job offer”.

@@

The function ${\allleadsto}: I × \allhist → \set{\phi, ¬\phi, 0}$ associates to each individual and path an element of $\Phi$ or the special symbol $0$ representing the absence of a strict preference. That is, ${\allleadsto}(i, \alpha)$ represents the choice of $i$ following exposure to the arguemnts of $\alpha$, in order. The case ${\allleadsto}(i, \alpha) = 0$ is used to represent indifference.
The notation $\alpha \ileadsto \phi$ will be used to mean ${\allleadsto}(i, \alpha) = \phi$, considering ${\ileadsto} \subseteq \allhist × \Phi$ as a binary relation.
As usual with binary relations, $\hist \nileadsto \prop$ means ${\allleadsto}(i, \alpha) ≠ \prop$ or equivalently ${\allleadsto}(i, \alpha) \in \set{\nprop, 0}$.

>>>>

\section{Exposure protocol and deliberated choice}
I assume given two antagonistic acts, constituting the decision at stake, such as “buy this object for the price of \$15” and “do not buy this object for the price of \$15”, or “take this job offer” and “decline this job offer”.
%The letter $\phi$ will be used to denote a generic act (one of these two), and given an act $\phi$, $¬\phi$ denotes the other act.
Let the set $P = \set{\phi, ¬\phi, 0}$ denote the set of possible preferences, where $\phi$ denote a strict preference for the first act against the other one, $¬\phi$ conversely, and $0$ denotes indifference (both acts are considered equally worth).

@@

The function ${\allleadsto}: I × \allhist → P$ associates to each individual and path an element of $P$, ${\allleadsto}(i, \alpha)$ representing the choice of $i$ following exposure to the arguments of $\alpha$, in order. That is, ${\allleadsto}(i, \alpha) = \phi$ denotes that $i$ chooses the first act after exposure to $\alpha$, ${\allleadsto}(i, \alpha) = ¬\phi$ denotes $i$ choosing the second act and ${\allleadsto}(i, \alpha) = 0$ is used to represent indifference of $i$.
The notation $\alpha \ileadsto p$ will be used to mean ${\allleadsto}(i, \alpha) = p$, considering ${\ileadsto} \subseteq \allhist × P$ as a binary relation.
As usual with binary relations, $\hist \nileadsto p$ means ${\allleadsto}(i, \alpha) ≠ p$ or equivalently ${\allleadsto}(i, \alpha) \in P \setminus \set{p}$.
